### 2021-02-26 input/background.tex
wip
mostly about AS

Fog infrastructures are distributed systems comprising heterogeneous
machines interconnected by communication links.

\begin{definition}[Fog infrastructure]
  A fog infrastructure is a \underline{g}raph $G(V, E)$ of
  \underline{v}ertices $V$ and bidirectional \underline{e}dges $E \in
  V \times V$. Edges have symmetric \underline{w}eights $w_{ij} =
  w_{ij}$ with $i, j \in V$.
\end{definition}

@@

Processes belong to logical partitions depending on path lengths. When
weights are latency or hop numbers, the optimal partitioning consists
in processing the multiple destinations shortest path at each process
\REF.

@@

@@

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:addA}Both Process $a$ and
      Process $c$ initiate a partition.
      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figaddA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:addB}Messages transit through communication
      links and carry increasing weights.]{\input{input/figaddB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:addC}Process $b$ receives and forwards
      $\alpha_{c}^{1}$ then discards $\alpha_{a}^{1.5}$, for the latter distance
      is higher.]{\input{input/figaddC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:addD}Processes $b$, $c$, and $d$ discard
      incoming messages. The system converged to optimal partitions.]{
      \input{input/figaddD.tex}}
    \caption{\label{fig:add}Simple accumulation in messages makes the
      system converge to optimal partitions with scoped flooding.}
  \end{center}
\end{figure*}

@@

\TODO{Figure~\ref{fig:del} shows that.}

@@

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:delA}Both Process $a$ and
      Process $c$ initiate then remove a partition.
      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figdelA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:delB}Process $b$ and Process $d$ receive and deliver
      messages based on their weights. $a$'s partition propagates to all processes.]
             {\input{input/figdelB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:delC}Process $c$'s partition reach $b$ and $d$.
      Its removal shortly follows. Process $b$ does not have any control
      information about partitions any more.]{\input{input/figdelC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:delD}Processes discard remaining messages.
      Process $b$ does not deliver $\delta_a$, for it already removed $a$ when
      Partition $c$ dominated it. Processes $c$ and $d$ remain in an incorrect
      partition.]{\input{input/figdelD.tex}}
  \end{center}
  \caption{\label{fig:del}Partition removals cannot rely only on
    current partition, for it may lead to either inconsistent
    partitioning, or every process receiving every broadcast.}
\end{figure*}

@@

\TODO{Dynamic Multiple-sources All-destinations shortest path on
  dynamic graphs?}

>>>>

Fog infrastructures are distributed systems comprising heterogeneous
machines interconnected by communication links. We do not consider
byzantine processes.

\begin{definition}[Fog infrastructure]
  A fog infrastructure is a \underline{g}raph $G(V, E)$ of
  \underline{v}ertices $V$ and bidirectional \underline{e}dges $E \in
  V \times V$. Edges have symmetric \underline{w}eights $w_{ij} =
  w_{ji}$ with $i, j \in V$.
\end{definition}

@@

Processes belong to logical partitions depending on path weights. When
weights are about latency or hop numbers, the optimal partitioning
consists in processing the multiple destinations shortest path at each
process \REF.

@@

\input{input/figdel.tex} %% figure positioning

@@

@@

Unfortunately, due to differences in receipt order of messages between
processes, stale information may stop prematurely the propagation of
relevant messages leading to inconsistent partitioning.
\TODO{Figure~\ref{fig:del} shows that.}

@@

@@

% \TODO{Dynamic Multiple-sources All-destinations shortest path on
%  dynamic graphs?}

\begin{figure}
  \begin{center}
    \input{input/figASmotivation.tex}
    \caption{\label{fig:ASmotivation}Scoped flooding extended to
      objects, processes do not know about all partitions that exist
      in the whole distributed system.}
  \end{center}
\end{figure}

To further improve scoped flooding in autonomous systems, processes
may belong to multiple partitions representing the objects they are
aware of. Figure~\ref{fig:ASmotivation} highlights the geo-distributed
nature of autonomous systems. Autonomous systems have topological
properties~\cite{nur2018geography} that processes can leverage to
avoid flooding the whole systems with control information about all
partitions. In Figure~\ref{fig:ASmotivation}, Process $e$ creates a
partition about a specific object, flooding Paris's AS to notify
neighboring processes of the object. However, it does not flood the
whole network, for control information stops at Process $b$. It
significantly saves bandwidth compared to broadcast since processes
below entrypoints of autonomous systems are order of magnitude more
numerous. Yet, Processes $c$ and $d$ know whom to ask when they need
to return an object they are unaware of. Processes remain efficient in
answering requests. \TODO{which is important for end users \REF.}

\begin{definition}[Partitions in asynchronous systems]
  Processes may hold multiple partitions \TODO{Use $\mathcal{P}$}
  \TODO{TODO}
\end{definition}

\begin{problem}[Consistent partitioning in AS]
  How to enable scoped flooding of objects in autonomous systems?
\end{problem}

### 2021-02-26 input/figASmotivation.tex
mostly about AS

  \draw (-1.5*\X, 0 - 5pt)
  node[below, circle, draw=black, fill=white, scale=0.35]{\large{0}}
  --  
  (-1.5*\X, \Y + 5pt)
  node[above, circle, draw=black, fill=white, scale=0.35]{\large{0}}; %% a - e

  \draw (-1.5*\X + 5pt, 0)
  node[right, circle, draw=black, fill=white, scale=0.35]{\large{1}}
  --
  (-1*\X, 0);

  \draw[dotted] (-1*\X, 0) -- (-0.5*\X, 0);

  \draw (-0.5*\X, 0)
  --  
  (0 - 5pt, 0)
  node[left, circle, draw=black, fill=white, scale=0.35]{\large{2}}; %% a - b

  \draw (0 +5pt, 0)
  node[right, circle, draw=black, fill=white, scale=0.35]{\large{1}}
  --
  (\X -5pt, 0)
  node[left, circle, draw=black, fill=white, scale=0.35]{\large{1}}; %% b - c

  \draw (0, 0 - 5pt)
  node[below, circle, draw=black, fill=white, scale=0.35]{\large{0}}
  --
  (0, \Y + 5pt)
  node[above, circle, draw=black, fill=white, scale=0.35]{\large{0}}; %% b - d

  \draw (\X + 3pt, 0 - 5pt)
  node[below left, circle, draw=black, fill=white, scale=0.35]{\large{0}}
  --
  (0 + 5pt, \Y - 3pt)
  node[above right, circle, draw=black, fill=white, scale=0.35]{\large{0}}; %% c - d

  \draw[dashed] (-0.75*\X, -0.5*\Y) -- (-0.75*\X, 1.5*\Y)
  node[above left]{\textit{AS 1}}
  node[above right]{\textit{AS 2}};

>>>>

  \draw (-1.5*\X, \Y + 5pt)
  -- node[above, font=\scriptsize, sloped]{$10ms$}
  (-1.5*\X, 0 - 5pt); %% a-e

  \draw (-1.5*\X + 5pt, 0)
  --
  (-1*\X, 0);

  \draw[dotted] (-1*\X, 0) --
  node[above, font=\scriptsize]{$300ms$} (-0.5*\X, 0);

  \draw (-0.5*\X, 0)
  --  
  (0 - 5pt, 0); %% a - b

  \draw (0 +5pt, 0)
  -- node[above, font=\scriptsize, sloped]{$15ms$}  
  (\X -5pt, 0); %% b - c

  \draw (0, \Y + 5pt)
  -- node[above, font=\scriptsize, sloped]{$20ms$}  
  (0, 0 - 5pt); %% b - d

  \draw (\X + 3pt, 0 - 5pt)
  -- node[above, font=\scriptsize, sloped]{$10ms$}  
  (0 + 5pt, \Y - 3pt); %% c - d

  \draw[dashed] (-0.75*\X, -0.5*\Y) -- (-0.75*\X, 1.5*\Y)
  node[above left]{\textit{(FR) Paris -- AS 1 \vphantom{g}}}
  node[above right]{\textit{AS 2 -- Wellington (NZ)}};

### 2021-02-26 input/proposal.tex
mostly about AS

This section describes \NAME's components and algorithms. First, it
starts by detailing a logical partitioning protocol in static
network. Second, it extends such protocol to dynamic systems. Last, it
describes an optimization based on Bloom filter.

To ease the reasoning about inter-AS dynamic partitioning in dynamic
networks, \NAME runs an independant broadcast protocol for each
object, and for each rank of links.  \TODO{Not so easy\ldots}
\TODO{Write and describe algo.} \TODO{Overhead of separating things,
  slightly more memory, but traffic wise? slower ?}  \TODO{In the
  example, not only Process $b$ keeps $e_1$ as its best partition, but
  it keeps it for links of rank 0, and links of rank 1.}

The rest of this section describes our proposal to solve these smaller
scientific problems. It first tackles dynamic partitions where
processes can add or delete partitions resulting in stale information
that may impair correctness. It then tackles dynamic networks where
edges appear and disappear at any time resulting in invalid
information that may impair correctness.

@@

>>>>

This section describes \NAME's components and algorithms. First, it
starts by detailing a logical partitioning protocol in static
network. Second, it extends such protocol to dynamic systems. Last, it
describes an optimization based on Bloom filter. \TODO{More more
  more. Thousands of pages paper it seems.}

@@

To ease the reasoning about inter-AS dynamic partitioning in dynamic
networks, \NAME runs an independant broadcast protocol for each
object, and for each rank of links.  \TODO{Not so easy\ldots}
\TODO{Write and describe algo.} \TODO{Overhead of separating things,
  slightly more memory, but traffic wise? slower ?}  \TODO{In the
  example, not only Process $b$ keeps $e_1$ as its best partition, but
  it keeps it for links of rank 0, and links of rank 1.}  When there
are no ranking in links, processes solely rely on
Algorithm~\ref{algo:adddelundo} for optimal partitioning.
